---
title: "ANLY503 A5"
author: "Lin Meng"
date: "2021/10/21"
output: html_document
---



```{r, echo=FALSE}
#htmltools::includeHTML("plotly.html")
#shiny::includeHTML("plotly.html")

```

```{r, echo=FALSE}
#cat("\n\n")
#htmltools::includeHTML("altair.html")
#shiny::includeHTML("altair.html")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Question 1 
In Question 1, I want to know the 8 parts with highest electricity consumption is same or not in the total consumption in the second half of 2012 or in each month of second half of 2012. To answer this question, I decide to create a pie chart, because pie chart is a good option for compare the total value and the percentage in the total value. There are 6 months and total second half month. Hence there are 7 pie plots need to create. To make the 7 pie plots easy to read, I decide to create an interactive pie plot with animation slides. In the first 6 slides, there are the 8 texts about the six months from July 2012 to December 2012. The last slide is about the slides each part of total consumption in the second half year of 2012. Also, the text in pie char will include both the value and percentage to read. On the hand, I decide to make the legend can be selected which can help people to choose the parts which they are interested in and unselect the parts which they have zero interests.<br>
From the below pie plots, in each month and total 6-month, freezer always be the part which have the highest electricity consumption. Except December, the second highest consumption and third highest consumption will be entertainment or fridge. In the December, the second higher consumption is lamp. Tablet always be the part with the least electricity consumption. In the conclusion, the highest consumption part (Freezer) and the least consumption part (Tablet) are always to be same. The middles are always changed. 
<iframe src="plotly.html" height=800px width=800px></iframe>


## Question 2
In question 2, I want to know whether the electricity consumption of each part was changing on dates from July 2012 to December 2012 and whether is there a specific date with highest consumption or least consumption for all 8 parts. To answer this question, I decide to create an interactive multiple lines plot, because line plot is a good choice to check the increase and decrease. There is a shortage of line plot. It’s hard to check the value of a specific point in a line. Hence, I decide to add a line which can show all the value for each line at same value of x axis. Since I show each day of half year and the value of electric consumption of freezer is much higher than other parts, I decide to add zoom and drag option into this plot. It can help people to check the value. 
<br>

<iframe src="altair.html" height=800px width=1200px></iframe>